### 2009-04-06 talk/icooolps2009-dotnet/benchmarks.tex
fix another XXX, and some other small fixes

To measure the performances of the CLI JIT backend, we wrote a simple virtual
machine for a dynamic toy languaged, called \emph{TLC}.

@@

\anto{XXX: explain which temp objects are created}
When doing plain interpretation, we need to create and destroy three temporary
objects at each iteration.  By contrast, the code generated by the JIT does
much better.  At the first iteration, the classes of the two operands of the
multiplication are promoted; then, the JIT compiler knows that both are
integers, so it can inline the code to compute the result.  Moreover, it can
\emph{virtualize} (see Section \ref{sec:virtuals}) all the temporary objects, because they never escape from
the inner loop.  The same remarks apply to the other two operations inside
the loop.

>>>>

To measure the performances of the CLI JIT backend, we wrote a simple virtual
machine for a dynamic toy language, called \emph{TLC}.

@@

When doing plain interpretation, we need to create and destroy three temporary
objects (the results of each operation) at each iteration.  By contrast, the code generated by the JIT does
much better.  At the first iteration, the classes of the two operands of the
multiplication go through a flexswitch; then, the JIT compiler knows that both are
integers, so it can inline the code to compute the result.  Moreover, thanks to escape analysis,
it can remove the allocation of all the temporary objects, because they never escape from
the inner loop.  The same remarks apply to the other two operations inside
the loop.
